\documentclass[10pt]{safecv}%

\cfoot{}
\setitemize{topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=0pt,label={$\circ$}}
\titlespacing*{\section}{0pt}{1.5\baselineskip}{\baselineskip}

\begin{document}
\MakeUppercase{\textbf{Gray Calhoun}}
\hfill
\parbox[t][0pt]{5cm}{%
\hfill (858) 361-4248 \\
\hfill \url{http://gray.clhn.org}\\
\hfill \href{https://www.linkedin.com/in/grayclhn}{linkedin.com/in/grayclhn} \\
\hfill \url{gray@clhn.org}
}

\vspace{\itemsep}%
Resume, \today

\section*{Recent work experience}

\begin{description}
\item[2020--present.] Principal Economist at Amazon
  \begin{itemize}
  \item Design major new machine learning products to support
    substantial business innovation in Private Brands and vendor
    negotiations -- provide science vision and framework, collaborate
    with product leads and business partners to set priorities and
    roadmap, and present product proposals for review at VP and SVP
    levels.
  \item Support several small science and engineering teams (5--15
    people each) developing machine and reinforcement learning
    products (e.g. providing technical review and sign-off on major
    scientific decisions; coaching managers, scientists, and engineers
    on appropriate modeling strategies, project roadmap and risk
    mitigation, hiring and developing scientists, and stakeholder
    engagement; mentoring junior and senior scientists).
  \end{itemize}
\item[2017--2020.] Senior Economist at Amazon
  \begin{itemize}
  \item Led small teams of 3-5 scientists to develop econometric
    models and machine and reinforcement learning algorithms to solve
    ambiguous, time-sensitive, and high-impact business problems in
    multiple domains (logistics, financial forecasting, macroeconomic
    shocks, and advertising, among others).
  \item Collaborate with engineering and product teams to develop and
    launch those systems.
  \item Communicate complex economic analysis and scientific results
    to business partners and leadership to support strategic decisions
    at VP, SVP, and CEO level (ongoing).
  \item Organized company-wide scientific programs -- technical
    review; internal conferences and seminars; educational lectures
    and training; etc.\ (ongoing).
  \item Coordinator for economist technical recruiting -- revised
    company-wide hiring guidelines and interview structure; onboarded
    \& trained new interviewers; conducted 70+ interviews.
  \end{itemize}
\item[2009--2017.] Assistant Professor of Economics, Iowa State University
  \begin{itemize}
  \item Published research in econometrics, primarily time
    series, forecasting, and the bootstrap; with secondary interests
    in macroecnomics and data visualization.
   \item Taught PhD Econometrics (first year introductory course and
     a time-series elective) and undergraduate macroeconomics (lectures up to 350 students); advised
     graduate students in Economics and Statistics departments.
   \item See \url{http://gray.clhn.org/dl/calhoun-cv.pdf} for complete
     academic CV.
   \end{itemize}
\end{description}

\section*{Education}

\begin{description}[noitemsep]
\item[2009.] PhD Economics. University of California, San Diego
\item[2006.] \allcaps{MS} Statistics. University of California, San Diego
\item[2001.] \allcaps{BA} Mathematics. Tufts University
\end{description}

\section*{Peer-reviewed Publications}

\begin{itemize}[noitemsep]
\item Block bootstrap consistency under weak assumptions.
  \textit{Econometric Theory}, 34(6):1383--1406, 2018
\item Integrated Assessment Models of the Food, Energy, and Water
  (\allcaps{FEW}) Nexus: A Review and Research Needs (with Catherine
  L.\ Kling, Raymond W.\ Arritt, and David A.\ Keiser). \textit{Annual
    Review of Resource Economics}, \mbox{9:143--163, 2017}
\item Bootstrap Confidence Intervals for Sharp Regression
  Discontinuity Designs (with Ot\'avio Bartalotti and Yang
  He). \textit{Advances in Econometrics}, 38:421--453, 2016
\item Hypothesis testing for linear regression when
  \textit{k}/\textit{n} is large. \textit{Journal of Econometrics},
  165(2):163--174, 2011
\end{itemize}

\section*{Other}

\begin{itemize}[noitemsep]
\item Programming skills: R, Julia, SQL, Python, Matlab, and other statistical and scientific
  programming languages.
\item See \url{https://github.com/grayclhn} for code repositories and artifacts (pre-Amazon).
\item See \url{https://scholar.google.com/citations?user=OS8d9ycAAAAJ} for additional research papers (pre-Amazon).
\end{itemize}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
